Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-01 scnn.tex
add pooling

\subsection{Coarsening}
\assign{Nathanaël}

How we get coarser or finer sampling of the sphere with Healpix. The $2^k \cdot 12$ points.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
\caption{Pooling, 1/12 of the sphere, 2 levels, molview projection.}
\label{fig:pooling}
\end{figure}

>>>>

\subsection{Coarsening}
The HealPix sampling present the advantage to have a natural corsening method
based on its construction. Each nside level divides each pixel into 4 subpixels.
We define the pooling process as the inverse operation grouping the 4 subpixels.
Figure~\ref{fig:pooling} illustrates the process.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
\caption{Pooling illustration for 2 levels using some part of the the mollview projection. 
The final patch represent 1/12 of the sphere.}
\label{fig:pooling}
\end{figure}
